---
title: "All Species Maps"
output: html_document
date: "2023-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

The objective of this Rmd is to develop figures for the publication.

Packages
```{r}
library(tidyverse)
library(terra)
library(ggplot2)
library(ggmap)
library(cowplot)
library(rnaturalearth)
library(tidyterra)
library(ggrepel)
library(ggpubr)
```

File paths
```{r}
base_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/mean_index/"
base_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/counts/"
max_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_max/mean_index/"
max_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_max/counts/"
min_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_min/mean_index/"
min_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_min/counts/"
#state_shapes_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_shapes/"
states_list_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_waters/"
zeros_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/zeros/rasters/"
depth_raster_path <- "/home/shares/aquaculture/AOA_climate_change/pressure_prep/"

```

Set up state outlines
```{r}
state_list <- terra::vect(x = paste0(states_list_path, "state_waters.shp"))
state_list <- state_list$state
state_list <- state_list[!str_detect(state_list, pattern = "Florida")]
state_list <- c(state_list, "Florida")

USA_state_shapes <- ne_states(iso_a2 = "US", returnclass = "sf")

USA_state_shapes <- USA_state_shapes %>% 
  select(name, postal, geometry) %>% 
  filter(stringr::str_detect(string = name,            
                    pattern = paste(state_list, collapse = "|")))

project_crs <- crs(terra::rast(x = paste0(base_index_results_path, "mean_index_performance_126_2011_2030.tif")))

USA_state_shapes <- terra::vect(USA_state_shapes)
crs(USA_state_shapes) <- project_crs

USA_state_shapes <- terra::crop(x = USA_state_shapes,
                                y = terra::rast(x = paste0(base_index_results_path, "mean_index_performance_126_2011_2030.tif")))


```

Set up the zeros data for change calculations and the depth mask
```{r}
depth_mask <- terra::rast(paste0(depth_raster_path, "depth_200m.tif" ))

zeros_data <- terra::rast(paste0(zeros_path, "federal_eez_zeros.tif"))

zeros_data <- terra::mask(x = zeros_data,
                          mask = depth_mask)

```

## Map scales
determined through map_scales_determination.Rmd in the max_min_difference_maps folder
```{r}
## index maps limits
current_index_limits <- c(0, 0.75)
current_index_breaks <- c(0, .25, .50, .75)

change_index_limits <- c(-.10, .10)
change_index_breaks <- c(-.10, -.05, 0, .05, .10)

# count limits setup for all species
all_species_current_count_limits <- c(0, 20)
all_species_current_count_breaks <- c(0, 5, 10, 15, 20)

all_species_change_count_limits <- c(-6, 6)
all_species_change_count_breaks <- c(-6, 0, 6)

# count limits setup for taxa
taxa_current_count_limits <- c(0, 10)
taxa_current_count_breaks <- c(0, 2, 4, 6, 8, 10)

taxa_change_count_limits <- c(-12, 12)
taxa_change_count_breaks <- c(-12, -6, 0, 6, 12)
```

## Function to make plots
```{r}
make_change_plots <- function(all_species_or_taxa, max_or_min, scenario, time_period, index_or_count){
  ## RASTER MANIPULATION
  # Establish limits based of all_species_or_taxa and index_or_count
  if (index_or_count == "index" & all_species_or_taxa == "all_species") {
    change_limits <- c(-.10, .10)
    change_breaks <- c(-.10, -.05, 0, .05, .10)
  } else if (index_or_count == "index" & all_species_or_taxa != "all_species") {
    change_limits <- c(-.20, .20)
    change_breaks <- c(-.20, -.10, 0, .10, .20)
  } else if (index_or_count == "count" & all_species_or_taxa == "all_species") {
    change_limits <- c(-10, 10)
    change_breaks <- c(-10, -5, 0, 5, 10)
  } else if (index_or_count == "count" & all_species_or_taxa != "all_species") {
    change_limits <- c(-6, 6)
    change_breaks <- c(-6, -3, 0, 3, 6)
  }
  
  # retrieve the results paths based on inputs
  if (index_or_count == "index" & max_or_min == "max") {
    base_results_path <- base_index_results_path
    new_results_path <- max_index_results_path
  } else if (index_or_count == "count" & max_or_min == "max") {
    base_results_path <- base_count_results_path
    new_results_path <- max_count_results_path
  } else if (index_or_count == "index" & max_or_min == "min") {
    base_results_path <- base_index_results_path
    new_results_path <- min_index_results_path
  } else if (index_or_count == "count" & max_or_min == "min") {
    base_results_path <- base_count_results_path
    new_results_path <- min_count_results_path
  }
  
  # make the file name using the inputs
  # this should be the same name for both files
  if (index_or_count == "index") {
    results_file_name <- paste0("mean_index_performance_", scenario, "_", time_period, ".tif")
  } else if (index_or_count == "count") {
    results_file_name <- paste0("count_", scenario, "_", time_period, ".tif")
  }
  
  # read in base and new results
  base_results_raster <- terra::rast(x = paste0(base_results_path, results_file_name))
  # mask to depth
  base_results_raster <- terra::mask(x = base_results_raster,
                                     mask = depth_mask)
  
  new_results_raster <- terra::rast(x = paste0(new_results_path, results_file_name))
  # mask to depth
  new_results_raster <- terra::mask(x = new_results_raster,
                                    mask = depth_mask)
  
  # calculate the differences between the results and save
  change_from_base_to_max_or_min <- sum(new_results_raster, zeros_data) - sum(base_results_raster, zeros_data)
  
  # Add in the limits if applying
  # change_from_base_to_max_or_min <- ifel(test = change_from_base_to_max_or_min > change_index_limits[2],
  #                                        yes = change_index_limits[2],
  #                                        no = ifel(change_from_base_to_max_or_min < change_index_limits[1],
  #                                                  yes = change_index_limits[1],
  #                                                  no = change_from_base_to_max_or_min))
  # summary(change_from_base_to_max_or_min)
  
  # subset raster for species/taxa for index or count
  if (index_or_count == "index") {
    change_from_base_to_max_or_min <- terra::subset(x = change_from_base_to_max_or_min,
                                                    subset = paste0(all_species_or_taxa, "_mean_index"))
  } else if (index_or_count == "count") {
    change_from_base_to_max_or_min <- terra::subset(x = change_from_base_to_max_or_min,
                                                    subset = paste0(all_species_or_taxa, "_count"))
  }
  
  #######
  # Make Mainland Plot
  # xlow, xhigh, ylow, yhigh
  mainland_ext <- c(-127, -60, 24, 50)
  
  # load main raster
  mainland_raster <- crop(x = change_from_base_to_max_or_min,
                          y = mainland_ext)
  
  # remove non-mainland states
  mainland_states <- USA_state_shapes %>% 
    filter(!name %in% c("Alaska", "Hawaii"))
  
  # retrieve small states centroids for labeling
  MD_DE_NJ_RI <- mainland_states %>% 
    filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
    centroids() %>% 
    as.data.frame(geom = "XY")
  
  # Choose palette and direction for maps
  pal <- "muted" #previous palette: "bl_yl_rd"
  dir <- -1 # previous direction: -1
  
  mainland_change <- ggplot() +
    # pull in the raster data
    geom_spatraster(data = mainland_raster) +
    # fill in scale details and color of background
    scale_fill_whitebox_c(palette = pal,
                          direction = dir,
                          # no breaks/limits for now
                          limits = change_limits,
                          breaks = change_breaks,
                          #background color fill
                          na.value = "grey80",
                          name = paste0("Change \n", str_to_title(index_or_count))) +
    #remove x y breaks
    scale_x_continuous(labels = NULL, breaks = 0) + 
    scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
    # remove x y labels as they are coordinates
    labs(x = "",
         y = "") +
    # add in the state boundary lines
    geom_spatvector(data = mainland_states,
                    alpha = 0.6,
                    fill = "white",
                    color = "#7d7d7d") +
    theme_void()+
    theme(# change the legend position and direction
      legend.position = c(.9,.3),
      legend.direction = "vertical",
      plot.title.position = "panel",
      # background color
      panel.background = element_rect(fill = "white", 
                                      color = NA),
      panel.border = element_rect(colour = NA, fill=NA))+  
    ggtitle(paste0("      Change from Mean Temperature ", str_to_title(index_or_count), " Results for ", str_to_title(str_replace(all_species_or_taxa, "_", " ")), " to ", str_to_title(max_or_min), "\n      Temperature Results for SSP ", scenario, " from ", str_replace(time_period, "_", "-"))) +
    # add in labels for states
    geom_spatvector_text(data = mainland_states %>% 
                           filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                         aes(label = postal),
                         alpha = 0.5,
                         size = 2.5)+
    # add in labels for states that need to be moved a bit
    geom_text_repel(data = MD_DE_NJ_RI,
                    aes(x = x,
                        y = y,
                        label = postal),
                    # order of nudges: MD, DE, NJ, RI
                    nudge_x = c(-1.5,-1, -0.5,0),
                    nudge_y = c(1.5,1.5,1.5,-1.5),
                    alpha = 0.5,
                    size = 2.5) 
  
  #######
  # Make Alaska plot
  # xlow, xhigh, ylow, yhigh
  alaska_ext <- c(-188, -129, 50, 94)
  
  alaska_raster <- crop(x = change_from_base_to_max_or_min,
                        y = alaska_ext)
  
  # isolate Alaska shape
  alaska_states <- USA_state_shapes %>% 
    filter(name %in% c("Alaska"))
  
  alaska_plot <- ggplot() +
    # pull in the raster data
    geom_spatraster(data = alaska_raster) +
    # fill in scale details and color of background
    scale_fill_whitebox_c(palette = pal,
                          direction = dir,
                          limits = change_limits,
                          breaks = change_breaks,
                          # background color fill
                          na.value = "grey80") +
    #remove x y breaks
    scale_x_continuous(labels = NULL, breaks = 0) +
    scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
    # remove x y labels as they are coordinates
    labs(x = "",
         y = "") +
    # add in the state boundary lines
    geom_spatvector(data = alaska_states,
                    alpha = 0.6,
                    fill = "white",
                    color = "#7d7d7d") +
    theme_void()+
    # don't show the legend since we are adding this to our mainland figure
    theme(legend.position = "none",
          # background color
          panel.background = element_rect(fill = "grey80"))+  
    #make a border
    theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
    # add in the alaska label
    geom_spatvector_text(data = alaska_states,
                         aes(label = postal),
                         alpha = 0.5,
                         size = 2.5,
                         nudge_y = 1)
  
  ##### 
  # make Hawaii plot
  # xlow, xhigh, ylow, yhigh
  hawaii_ext <- c(-166, -154, 15, 25)
  
  hawaii_raster <- crop(x = change_from_base_to_max_or_min,
                        y = hawaii_ext)
  # isolate Hawaii shape
  hawaii_states <- USA_state_shapes %>% 
    filter(name %in% c("Hawaii"))
  
  hawaii_states <- crop(x = hawaii_states,
                        y = hawaii_ext)
  
  hawaii_plot <- ggplot() +
    # pull in the raster data
    geom_spatraster(data = hawaii_raster) +
    # fill in scale details and color of background
    scale_fill_whitebox_c(palette = pal,
                          direction = dir,
                          limits = change_limits,
                          breaks = change_breaks,
                          # background color fill
                          na.value = "grey80") +
    #remove x y breaks
    scale_x_continuous(labels = NULL, breaks = 0) +
    scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
    # remove x y labels as they are coordinates
    labs(x = "",
         y = "") +
    # add in the state boundary lines
    geom_spatvector(data = hawaii_states,
                    alpha = 0.6,
                    fill = "white",
                    color = "#7d7d7d") +
    theme_void()+
    # don't show the legend since we are adding this to our mainland figure
    theme(legend.position = "none",
          # background color
          panel.background = element_rect(fill = "grey80"),
          # add in a border
          panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
    geom_spatvector_text(data = hawaii_states,
                         aes(label = postal),
                         alpha = 0.5,
                         size = 2.5,
                         nudge_y = 1,
                         nudge_x = -8)
  
  ######
  #Put all plots together and save
  change_plot <-
    ggdraw() +
    draw_plot(mainland_change) +
    draw_plot(alaska_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
    draw_plot(hawaii_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
    theme(panel.background = element_rect(fill = 'white',
                                          color = "white"),
          plot.background = element_rect(fill = 'white',
                                         color = "white")) 
  
  # NOTE: this does not match the look of the saved output
  change_plot
  
  figure_save_path <- file.path("/home/shares/aquaculture/AOA_climate_change/figures/max_and_min_temp_change_for_review", max_or_min, index_or_count)
  
  ggsave(plot = change_plot,
         filename = paste0(all_species_or_taxa, "_", scenario, "_", time_period,".pdf"),
         device = "pdf",
         path = figure_save_path,
         width = 7,
         height = 5,
         units = "in")
  
  print(paste("Done with", all_species_or_taxa, max_or_min, scenario, time_period, index_or_count))
}
```

Test function
```{r}
make_change_plots(all_species_or_taxa = "all_species", 
                  max_or_min = "max", 
                  scenario = "585", 
                  time_period = "2011_2030", 
                  index_or_count = "count")
```

## Loop through function for all parts

### Max temps and index
```{r, warning=FALSE}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")
SSP <- c("126", "245", "585")
spec_or_tax <- c("all_species", "mollusc", "seaweed", "fish")

for (i in 1:length(times)) {
  for (j in 1:length(SSP)) {
    for (k in 1:length(spec_or_tax)) {
      make_change_plots(all_species_or_taxa = spec_or_tax[k], 
                        max_or_min = "max", 
                        scenario = SSP[j], 
                        time_period = times[i], 
                        index_or_count = "index")
      
      print(paste0("Done with ", spec_or_tax[k]))
    }
    print(paste0("Done with ", SSP[j]))
  }
  print(paste0("Done with ", times[i]))
}
```

### Min temps and index
```{r, warning=FALSE}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")
SSP <- c("126", "245", "585")
spec_or_tax <- c("all_species", "mollusc", "seaweed", "fish")

for (i in 1:length(times)) {
  for (j in 1:length(SSP)) {
    for (k in 1:length(spec_or_tax)) {
      make_change_plots(all_species_or_taxa = spec_or_tax[k], 
                        max_or_min = "min", 
                        scenario = SSP[j], 
                        time_period = times[i], 
                        index_or_count = "index")
      
      print(paste0("Done with ", spec_or_tax[k]))
    }
    print(paste0("Done with ", SSP[j]))
  }
  print(paste0("Done with ", times[i]))
}
```

### max temps and count
```{r, warning=FALSE}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")
SSP <- c("126", "245", "585")
spec_or_tax <- c("all_species", "mollusc", "seaweed", "fish")

for (i in 1:length(times)) {
  for (j in 1:length(SSP)) {
    for (k in 1:length(spec_or_tax)) {
      make_change_plots(all_species_or_taxa = spec_or_tax[k], 
                        max_or_min = "max", 
                        scenario = SSP[j], 
                        time_period = times[i], 
                        index_or_count = "count")
      
    }
    print(paste0("Done with ", SSP[j]))
  }
  print(paste0("Done with ", times[i]))
}
```

### min temps and count
```{r, warning=FALSE}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")
SSP <- c("126", "245", "585")
spec_or_tax <- c("all_species", "mollusc", "seaweed", "fish")

for (i in 1:length(times)) {
  for (j in 1:length(SSP)) {
    for (k in 1:length(spec_or_tax)) {
      make_change_plots(all_species_or_taxa = spec_or_tax[k], 
                        max_or_min = "min", 
                        scenario = SSP[j], 
                        time_period = times[i], 
                        index_or_count = "count")
      
      print(paste0("Done with ", spec_or_tax[k]))
    }
    print(paste0("Done with ", SSP[j]))
  }
  print(paste0("Done with ", times[i]))
}
```

## Below part used to establish function to make sure it works
```{r}


all_species_or_taxa <- "all_species"
max_or_min <- "max"
scenario <- "585"
time_period <- "2011_2030"
index_or_count <- "count"

# Establish limits based on all_species_or_taxa and index_or_count
if (index_or_count == "index" & all_species_or_taxa == "all_species") {
  change_limits <- c(-.10, .10)
  change_breaks <- c(-.10, -.05, 0, .05, .10)
} else if (index_or_count == "index" & all_species_or_taxa != "all_species") {
  change_limits <- c(-.20, .20)
  change_breaks <- c(-.20, -.10, 0, .10, .20)
} else if (index_or_count == "count" & all_species_or_taxa == "all_species") {
  change_limits <- c(-10, 10)
  change_breaks <- c(-10, -5, 0, 5, 10)
} else if (index_or_count == "count" & all_species_or_taxa != "all_species") {
  change_limits <- c(-6, 6)
  change_breaks <- c(-6, -3, 0, 3, 6)
}

# retrieve the results paths based on inputs
if (index_or_count == "index" & max_or_min == "max") {
  base_results_path <- base_index_results_path
  new_results_path <- max_index_results_path
} else if (index_or_count == "count" & max_or_min == "max") {
  base_results_path <- base_count_results_path
  new_results_path <- max_count_results_path
} else if (index_or_count == "index" & max_or_min == "min") {
  base_results_path <- base_index_results_path
  new_results_path <- min_index_results_path
} else if (index_or_count == "count" & max_or_min == "min") {
  base_results_path <- base_count_results_path
  new_results_path <- min_count_results_path
}

# make the file name using the inputs
# this should be the same name for both files
if (index_or_count == "index") {
  results_file_name <- paste0("mean_index_performance_", scenario, "_", time_period, ".tif")
} else if (index_or_count == "count") {
  results_file_name <- paste0("count_", scenario, "_", time_period, ".tif")
}

# read in base and new results
base_results_raster <- terra::rast(x = paste0(base_results_path, results_file_name))
# mask to depth
base_results_raster <- terra::mask(x = base_results_raster,
                                   mask = depth_mask)

new_results_raster <- terra::rast(x = paste0(new_results_path, results_file_name))
# mask to depth
new_results_raster <- terra::mask(x = new_results_raster,
                                  mask = depth_mask)

# calculate the differences between the results and save
change_from_base_to_max_or_min <- sum(new_results_raster, zeros_data) - sum(base_results_raster, zeros_data)

# Add in the limits if applying
# change_from_base_to_max_or_min <- ifel(test = change_from_base_to_max_or_min > change_index_limits[2],
#                                        yes = change_index_limits[2],
#                                        no = ifel(change_from_base_to_max_or_min < change_index_limits[1],
#                                                  yes = change_index_limits[1],
#                                                  no = change_from_base_to_max_or_min))
# summary(change_from_base_to_max_or_min)

# subset raster for species/taxa for index or count
if (index_or_count == "index") {
  change_from_base_to_max_or_min <- terra::subset(x = change_from_base_to_max_or_min,
                                                  subset = paste0(all_species_or_taxa, "_mean_index"))
} else if (index_or_count == "count") {
  change_from_base_to_max_or_min <- terra::subset(x = change_from_base_to_max_or_min,
                                                  subset = paste0(all_species_or_taxa, "_count"))
}

```

### Mainland
```{r}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = change_from_base_to_max_or_min,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_change <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        # no breaks/limits for now
                        limits = change_limits,
                        breaks = change_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = paste0("Change \n", str_to_title(index_or_count))) +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle(paste0("      Change from Mean Temperature ", str_to_title(index_or_count), " Results for ", str_to_title(str_replace(all_species_or_taxa, "_", " ")), " to ", str_to_title(max_or_min), "\n      Temperature Results for SSP ", scenario, " from ", str_replace(time_period, "_", "-"))) +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_change
```

### Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = change_from_base_to_max_or_min,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_limits,
                        breaks = change_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
alaska_plot
```

### Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = change_from_base_to_max_or_min,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_limits,
                        breaks = change_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
hawaii_plot
```

### pull together plots
```{r}
change_plot <-
  ggdraw() +
  draw_plot(mainland_change) +
  draw_plot(alaska_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE: this does not match the look of the saved output
change_plot

figure_save_path <- file.path("/home/shares/aquaculture/AOA_climate_change/figures/max_and_min_temp_change_for_review", max_or_min, index_or_count)

# ggsave(plot = change_plot,
#        filename = paste0(all_species_or_taxa, "_", scenario, "_", time_period,".pdf"),
#        device = "pdf",
#        path = figure_save_path,
#        width = 7,
#        height = 5,
#        units = "in")
```



Data Set Up
```{r}
current_index <- terra::rast(x = paste0(index_results_path, "mean_index_performance_126_2011_2030.tif"))
current_index <- terra::mask(x = current_index,
                             mask = depth_mask)
current_index <- current_index$all_species_mean_index
current_index_df <- as.data.frame(current_index, xy = TRUE, cells = TRUE)

current_count <- terra::rast(x = paste0(count_results_path, "count_126_2011_2030.tif"))
current_count <- terra::mask(x = current_count,
                             mask = depth_mask)
current_count <- current_count$all_species_count
current_count_df <- as.data.frame(current_count, xy = TRUE, cells = TRUE)

# 245 Scenario
index_245_2051_2070 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_245_2051_2070.tif"))
index_245_2051_2070 <- terra::mask(x = index_245_2051_2070,
                                   mask = depth_mask)
index_245_2051_2070 <- index_245_2051_2070$all_species_mean_index
index_245_2051_2070_df <- as.data.frame(index_245_2051_2070, xy = TRUE, cells = TRUE)


count_245_2051_2070 <- terra::rast(x = paste0(count_results_path, "count_245_2051_2070.tif"))
count_245_2051_2070 <- terra::mask(x = count_245_2051_2070,
                                   mask = depth_mask)
count_245_2051_2070 <- count_245_2051_2070$all_species_count
count_245_2051_2070_df <- as.data.frame(count_245_2051_2070, xy = TRUE, cells = TRUE)


index_245_2071_2090 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_245_2071_2090.tif"))
index_245_2071_2090 <- terra::mask(x = index_245_2071_2090,
                                   mask = depth_mask)
index_245_2071_2090 <- index_245_2071_2090$all_species_mean_index
index_245_2071_2090_df <- as.data.frame(index_245_2071_2090, xy = TRUE, cells = TRUE)


count_245_2071_2090 <- terra::rast(x = paste0(count_results_path, "count_245_2071_2090.tif"))
count_245_2071_2090 <- terra::mask(x = count_245_2071_2090,
                                   mask = depth_mask)
count_245_2071_2090 <- count_245_2071_2090$all_species_count
count_245_2071_2090_df <- as.data.frame(count_245_2071_2090, xy = TRUE, cells = TRUE)

# 585 scenario
index_585_2051_2070 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_585_2051_2070.tif"))
index_585_2051_2070 <- terra::mask(x = index_585_2051_2070,
                                   mask = depth_mask)
index_585_2051_2070 <- index_585_2051_2070$all_species_mean_index
index_585_2051_2070_df <- as.data.frame(index_585_2051_2070, xy = TRUE, cells = TRUE)


count_585_2051_2070 <- terra::rast(x = paste0(count_results_path, "count_585_2051_2070.tif"))
count_585_2051_2070 <- terra::mask(x = count_585_2051_2070,
                                   mask = depth_mask)
count_585_2051_2070 <- count_585_2051_2070$all_species_count
count_585_2051_2070_df <- as.data.frame(count_585_2051_2070, xy = TRUE, cells = TRUE)


index_585_2071_2090 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_585_2071_2090.tif"))
index_585_2071_2090 <- terra::mask(x = index_585_2071_2090,
                                   mask = depth_mask)
index_585_2071_2090 <- index_585_2071_2090$all_species_mean_index
index_585_2071_2090_df <- as.data.frame(index_585_2071_2090, xy = TRUE, cells = TRUE)


count_585_2071_2090 <- terra::rast(x = paste0(count_results_path, "count_585_2071_2090.tif"))
count_585_2071_2090 <- terra::mask(x = count_585_2071_2090,
                                   mask = depth_mask)
count_585_2071_2090 <- count_585_2071_2090$all_species_count
count_585_2071_2090_df <- as.data.frame(count_585_2071_2090, xy = TRUE, cells = TRUE)
```
