---
title: "Maps breaks code"
output: html_document
date: "2023-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

The objective of this Rmd is to determine the best scales to use in the difference_maps_with_max_min script for the figures.

Packages
```{r}
library(tidyverse)
library(terra)
library(ggplot2)
library(ggmap)
library(cowplot)
library(rnaturalearth)
library(tidyterra)
library(ggrepel)
library(ggpubr)
```

File paths
```{r}
base_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/mean_index/"
base_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/counts/"
max_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_max/mean_index/"
max_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_max/counts/"
min_index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_min/mean_index/"
min_count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs_min/counts/"
#state_shapes_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_shapes/"
states_list_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_waters/"
zeros_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/zeros/rasters/"
figure_save_path <- "/home/shares/aquaculture/AOA_climate_change/figures/maps_for_each_taxa/seaweeds/"
depth_raster_path <- "/home/shares/aquaculture/AOA_climate_change/pressure_prep/"

```


Set up the zeros data for change calculations and the depth mask
```{r}
depth_mask <- terra::rast(paste0(depth_raster_path, "depth_200m.tif" ))

zeros_data <- terra::rast(paste0(zeros_path, "federal_eez_zeros.tif"))

zeros_data <- terra::mask(x = zeros_data,
                          mask = depth_mask)

```



### Map Scales - make function
```{r}
scenario <- "126"
time_period <- "2011_2030"
max_or_min <- "max"
index_or_count <- "index"

comparing_results <- function(scenario, time_period, max_or_min, index_or_count) {
  # retrieve the results paths based on inputs
  if (index_or_count == "index" & max_or_min == "max") {
    base_results_path <- base_index_results_path
    new_results_path <- max_index_results_path
  } else if (index_or_count == "count" & max_or_min == "max") {
    base_results_path <- base_count_results_path
    new_results_path <- max_count_results_path
  } else if (index_or_count == "index" & max_or_min == "min") {
    base_results_path <- base_index_results_path
    new_results_path <- min_index_results_path
  } else if (index_or_count == "count" & max_or_min == "min") {
    base_results_path <- base_count_results_path
    new_results_path <- min_count_results_path
  }
  
  # make the file name using the inputs
  # this should be the same name for both files
  if (index_or_count == "index") {
    results_file_name <- paste0("mean_index_performance_", scenario, "_", time_period, ".tif")
  } else if (index_or_count == "count") {
    results_file_name <- paste0("count_", scenario, "_", time_period, ".tif")
  }
  
  # read in base and new results
  base_results_raster <- terra::rast(x = paste0(base_results_path, results_file_name))
  # mask to depth
  base_results_raster <- terra::mask(x = base_results_raster,
                                     mask = depth_mask)
  
  new_results_raster <- terra::rast(x = paste0(new_results_path, results_file_name))
  # mask to depth
  new_results_raster <- terra::mask(x = new_results_raster,
                                    mask = depth_mask)
  
  # calculate the differences between the results and save
  summary_difference <- summary(sum(new_results_raster, zeros_data) - sum(base_results_raster, zeros_data))
  
  return(summary_difference)
}


```

## use function
### max index for scenario 126 and all  times

```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_index_126 <- comparing_results(scenario <- "126",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "index")
  print(max_index_126)
}

```
for all species min = -.07, max = 0.08

for taxa min = -.17, max = 0.19


### max index for scenario 245 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_index_245 <- comparing_results(scenario <- "245",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "index")
  print(max_index_245)
}

```
for all species min = -.07, max = 0.09

for taxa min = -.18, max = 0.20

### max index for scenario 585 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_index_585 <- comparing_results(scenario <- "585",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "index")
  print(max_index_585)
}

```
for all species min = -.08, max = 0.09

for taxa min = -.17, max = 0.18

### min index for scenario 126 and all  times

```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_index_126 <- comparing_results(scenario <- "126",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "index")
  print(min_index_126)
}

```
for all species min = -.09, max = 0.06

for taxa min = -.12, max = 0.13


### min index for scenario 245 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_index_245 <- comparing_results(scenario <- "245",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "index")
  print(min_index_245)
}

```
for all species min = -.08, max = 0.07

for taxa min = -.12, max = 0.14

### min index for scenario 585 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_index_585 <- comparing_results(scenario <- "585",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "index")
  print(min_index_585)
}

```
for all species min = -.09, max = 0.07

for taxa min = -.17, max = 0.14

#### for index
```{r}
all_species_limits <- c(-.10, .10)

taxa_limits <-c(-.20, .20)
```

### max count for scenario 126 and all  times

```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_count_126 <- comparing_results(scenario <- "126",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "count")
  print(max_count_126)
}

```
for all species min = -3, max = 8

for taxa min = -4, max = 6


### max count for scenario 245 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_count_245 <- comparing_results(scenario <- "245",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "count")
  print(max_count_245)
}

```
for all species min = -4, max = 8

for taxa min = -5, max = 6

### max count for scenario 585 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  max_count_585 <- comparing_results(scenario <- "585",
                                     time_period <- times[i],
                                     max_or_min <- "max",
                                     index_or_count <- "count")
  print(max_count_585)
}

```
for all species min = -3, max = 10

for taxa min = -5, max = 6

### min count for scenario 126 and all  times

```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_count_126 <- comparing_results(scenario <- "126",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "count")
  print(min_count_126)
}

```
for all species min = -9, max = 4

for taxa min = -5, max = 4


### min count for scenario 245 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_count_245 <- comparing_results(scenario <- "245",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "count")
  print(min_count_245)
}

```
for all species min = -9, max = 3

for taxa min = -6, max = 4

### min count for scenario 585 and all times
```{r}
times <- c("2011_2030", "2031_2050", "2051_2070", "2071_2090")

for (i in 1:length(times)) {
  min_count_585 <- comparing_results(scenario <- "585",
                                     time_period <- times[i],
                                     max_or_min <- "min",
                                     index_or_count <- "count")
  print(min_count_585)
}

```
for all species min = -9, max = 3

for taxa min = -6, max = 4

#### for count
```{r}
all_species_limits <- c(-10, 10)

taxa_limits <-c(-6, 6)
```

