---
title: "Untitled"
author: "Cat Fong"
date: "2023-07-06"
output: html_document
editor_options: 
  chunk_output_type: console
---

Objective:
The objective of this step is to take the species index performance data generated in `01_all_species+performance.Rmd` and aggregate it to mean performance of all species and each taxa and save the files for each scenario and time period.

Packages
```{r}
library(tidyverse)
library(terra)
```


File Paths
```{r}
performance_rasters_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/all_species_index/"
save_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/mean_index/"
```


Calculate species performance using the index method. A function is made to do this method for all species and by taxa.

```{r}
source(here::here("impact_calcs/custom_functions/aggregate_index_performance_maker.R"))

```


Apply function to all scenarios and time periods
```{r}
overwrite <- TRUE
performance_files <- list.files(path = performance_rasters_path,
                                pattern = "all_species_*")
number_files <- n_distinct(performance_files)

for (i in 1:number_files){
  scenario <- str_sub(string = performance_files[i],
                      start = 13,
                      end = 25)
  scenario_raster <- terra::rast(paste0(performance_rasters_path, performance_files[i]))
  
  scenario_raster <- aggregate_index_performance_maker(species_raster = scenario_raster)
  
  terra::writeRaster(x = scenario_raster,
                     filename = paste0(save_path, "mean_index_performance_", scenario, ".tif"),
                     gdal="COMPRESS=NONE",
                     overwrite = overwrite)
  print(paste("Done with", performance_files[i]))
}


```

did the above loop work as intended?
```{r}
mean_index_performance_126_2011_2030 <- terra::rast(paste0(save_path,"mean_index_performance_126_2011_2030.tif"))
mean_index_performance_126_2031_2050 <- terra::rast(paste0(save_path,"mean_index_performance_126_2031_2050.tif"))
mean_index_performance_126_2051_2070 <- terra::rast(paste0(save_path,"mean_index_performance_126_2051_2070.tif"))
mean_index_performance_126_2071_2090 <- terra::rast(paste0(save_path,"mean_index_performance_126_2071_2090.tif")) 

mean_index_performance_245_2011_2030 <- terra::rast(paste0(save_path,"mean_index_performance_245_2011_2030.tif"))
mean_index_performance_245_2031_2050 <- terra::rast(paste0(save_path,"mean_index_performance_245_2031_2050.tif"))
mean_index_performance_245_2051_2070 <- terra::rast(paste0(save_path,"mean_index_performance_245_2051_2070.tif"))
mean_index_performance_245_2071_2090 <- terra::rast(paste0(save_path,"mean_index_performance_245_2071_2090.tif")) 

mean_index_performance_585_2011_2030 <- terra::rast(paste0(save_path,"mean_index_performance_585_2011_2030.tif"))
mean_index_performance_585_2031_2050 <- terra::rast(paste0(save_path,"mean_index_performance_585_2031_2050.tif"))
mean_index_performance_585_2051_2070 <- terra::rast(paste0(save_path,"mean_index_performance_585_2051_2070.tif"))
mean_index_performance_585_2071_2090 <- terra::rast(paste0(save_path,"mean_index_performance_585_2071_2090.tif")) 



terra::plot(mean_index_performance_126_2011_2030)
```




