---
title: "state_permitted_species_filter"
output: html_document
date: "2023-07-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective  

The objective of this markdown is to filter the performance calculations by the species presently permitted for marine aquaculture in each state. Because we need to filter out different species for each state we need to restart the calculations from the output of `all_species_performance.Rmd`

Packages
```{r}
library(tidyverse)
library(terra)
library(janitor)
```

Data paths
```{r}
permitted_species_path <- "/home/shares/aquaculture/AOA_climate_change/raw_data/state_permitted_species/"
all_species_performance_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/all_species_index/"
states_shape_file_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_waters/"
example_raster_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_borders/rasters/"
depth_raster_path <- "/home/shares/aquaculture/AOA_climate_change/pressure_prep/"

```

## Clean up the permitted species data

```{r}
# read in raw species data
permitted_species_raw <- read.csv(paste0(permitted_species_path, "state_permitted_species_7_26_23.csv"))

# make a 1 column data frame of the species names from permitted_species_raw and clean them
species_names_clean <- janitor::make_clean_names(string = permitted_species_raw$Common.name) %>% 
  data.frame() 

# make column name common_name
colnames(species_names_clean) = "common_name"

# column bind the clean names with the raw data
permitted_species_clean <- cbind(species_names_clean, permitted_species_raw) %>% 
  # remove unclean Common.name columns
  select(-Common.name) %>% 
  # rename species.name and broad.taxa columns
  rename(scientific_name = species.name,
         taxa = broad.taxa) %>% 
  # pivot the table longer to be in tidy format and easier to work with
  pivot_longer(4:ncol(permitted_species_raw),
               names_to = "state",
               values_to = "species_permitted",
               values_drop_na = FALSE) %>% 
  # Replace periods in state names with spaces
  mutate(state = str_replace(state, pattern = "[.]", replacement = " ")) %>% 
  # make any value in species_permitted column true and and NA false
  mutate(species_permitted = if_else(condition = is.na(species_permitted),
                                     true = FALSE,
                                     false = TRUE))

# fix Delaware spelling
permitted_species_clean$state[permitted_species_clean$state == "Deleware"] <- "Delaware"

write.csv(x = permitted_species_clean,
          file = "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/permitted_species_clean.csv")

```

## Filter the all_species_performance data to state waters only
Using the same loop that was made in `state_boarder_filter.Rmd` the below chunk will mask the species performance rasters to their state waters.
```{r}
overwrite <- FALSE
save_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/all_species_state_borders/"

# read in state_waters shape file - this should not change
state_shapes <- terra::vect(paste0(states_shape_file_path, "state_waters.shp"))

# read in all_species_performance_path as our performance_file_path
performance_file_path <- all_species_performance_path

# choose result_type we are using for this section, this can change between "index" and "count"
result_type <- "index"

if (result_type == "index") {
  performance_file_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/all_species_index/"
} else {
  stop("result_type must only be index")
}

performance_files_list <- list.files(performance_file_path)

for (j in 1:n_distinct(performance_files_list)) {
  # read in results raster we are interested in
  results_raster <- terra::rast(paste0(performance_file_path, performance_files_list[j]))
  
  # apply depth mask raster to all areas and species, only areas with a depth < 200m are viable for aquaculture
  depth_mask <- terra::rast(paste0(depth_raster_path, "depth_200m.tif" ))
  
  results_raster <- terra::mask(x = results_raster,
                                mask = depth_mask)
  
  # make a list of the state
  state_list <- state_shapes$state
  # fix the two Floridas issue by removing Gulf and Pacfic Florida and adding in just Florida
  state_list <- state_list[!str_detect(state_list, pattern = "Florida")]
  state_list <- c(state_list, "Florida")
  
  # get the scenario name from the sourced tif file
  scenario_timeperiod <- str_sub(string = terra::sources(results_raster), 
                                 start = -17, 
                                 end = -5)
  # make empty df to add to
  all_states_df <- data.frame()
  #make empty raster with 4 layers
  all_states_raster <- terra::rast()
  
  for (i in 1:n_distinct(state_list)) {
    # retrieve the state name for the loop
    state_name <- state_list[i]
    
    # if the state name is Florida, combine the Gulf and Atlantic shapes
    if (state_name == "Florida") {
      state_results_raster <- terra::mask(x = results_raster,
                                          mask = state_shapes[state_shapes$state == c("Florida Gulf","Florida Atlantic")])
    } else{
      # else just state the state shape from the state_name
      state_results_raster <- terra::mask(x = results_raster,
                                          mask = state_shapes[state_shapes$state == state_name])
    }
    
    # if statement to make add first layers to all_state_rasters
    if (i == 1) {
      all_states_raster <- c(all_states_raster, state_results_raster)
    } else{
      # else use the merge function in terra to join the layers of matching names
      # using merge in areas where the SpatRaster objects overlap, the values of the SpatRaster that is last in the sequence of arguments will be retained. 
      all_states_raster <- terra::merge(x = all_states_raster,
                                        y = state_results_raster)
    }
    
    # make the state_df from the states_results raster
    state_df <- as.data.frame(x = state_results_raster,
                              xy = TRUE)
    
    # add state name column
    state_df <- state_df %>% 
      mutate(state = state_name)
    
    # add to empty df of all states
    all_states_df <- rbind(all_states_df, state_df)
    
    # remove any state border rows that may have joined in df
    all_states_df <- all_states_df %>% 
      unique()
    
    print(paste("Done with", state_name))
  }
  
  # save the raster file
  terra::writeRaster(x = all_states_raster,
                     filename = paste0(save_path, "rasters/", "all_species_state_borders_", result_type,"_",scenario_timeperiod, ".tif"),
                     gdal="COMPRESS=NONE",
                     overwrite = overwrite)
  
  # save the data frame as a csv
  write.csv(x = all_states_df,
            file = paste0(save_path, "data_frames/", "all_species_state_borders_", result_type,"_",scenario_timeperiod, ".csv"))
  
  print(paste("Done with", performance_files_list[j]))
}

```

### Make an empty rasters with the 4 layers we want
```{r}
overwrite <- TRUE
# read in a raster we have made to use as a template, we want the layer names
empty_index_raster_raw <- terra::rast(paste0(example_raster_path, "index/index_126_2011_2030.tif"))

# make template raster empty
empty_index_raster_clean <- terra::ifel(test = empty_index_raster_raw >= 0,
                                  yes = NA,
                                  no = NA)

terra::writeRaster(x = empty_index_raster_clean,
                   filename = "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/empty_index_raster_template.tif",
                   gdal="COMPRESS=NONE",
                   overwrite = overwrite)

# read in a raster we have made to use as a template, we want the layer names
empty_count_raster_raw <- terra::rast(paste0(example_raster_path, "count/count_126_2011_2030.tif"))

# make template raster empty
empty_count_raster_clean <- terra::ifel(test = empty_count_raster_raw >= 0,
                                  yes = NA,
                                  no = NA)

terra::writeRaster(x = empty_count_raster_clean,
                   filename = "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/empty_count_raster_template.tif",
                   gdal="COMPRESS=NONE",
                   overwrite = overwrite)

```


## Filter all the species data to each state and calculate index and count
```{r}
# make a save path for the output from this section
save_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/"
overwrite <- TRUE

### source custom functions needed
source("~/AOA_climate_change/impact_calcs/custom_functions/aggregate_index_performance_maker.R", echo = FALSE, verbose = FALSE)
source("~/AOA_climate_change/impact_calcs/custom_functions/aggregate_count_performance_maker.R", echo = FALSE, verbose = FALSE)
source("~/AOA_climate_change/impact_calcs/custom_functions/all_species_aggregate_index_performance_maker.R", echo = FALSE, verbose = FALSE)

all_species_state_borders_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/all_species_state_borders/rasters/"
all_species_state_borders_list <- list.files(all_species_state_borders_path)

# read in the clean permitted species data
permitted_species_clean <- read.csv(file = "/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/permitted_species_clean.csv") %>% 
  select(-X)

# read in state_waters shape file - this should not change
state_shapes <- terra::vect(paste0(states_shape_file_path, "state_waters.shp"))

for (j in 1:n_distinct(all_species_state_borders_list)) {
  # read in results raster we are interested in
  results_raster <- terra::rast(x = paste0(all_species_state_borders_path, all_species_state_borders_list[j]))
  
  # make a list of the state
  state_list <- state_shapes$state
  # fix the two Floridas issue by removing Gulf and Pacfic Florida and adding in just Florida
  state_list <- state_list[!str_detect(state_list, pattern = "Florida")]
  state_list <- c(state_list, "Florida")
  
  # get the scenario name from the sourced tif file
  scenario_timeperiod <- str_sub(string = terra::sources(results_raster), 
                                 start = -17, 
                                 end = -5)
  # # make empty df to add to
  # all_states_df <- data.frame()
  # #make empty rasters and df with 4 layers
  all_states_index_raster <- terra::rast("/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/empty_index_raster_template.tif")
  all_states_index_df <- data.frame()
  all_states_total_species_index_raster <- terra::rast("/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/empty_index_raster_template.tif")
  all_states_total_species_index_df <- data.frame()
  all_states_count_raster <- terra::rast("/home/shares/aquaculture/AOA_climate_change/performance_calcs/state_permitted_species/empty_count_raster_template.tif")
  all_states_count_df <- data.frame()
  
  for (i in 1:n_distinct(state_list)) {
    # retrieve the state name for the loop
    state_name <- state_list[i]
    
    # filter for the state in the permitted_species_clean df and only species allowed by the state
    state_permitted_species <- permitted_species_clean %>% 
      filter(state == state_name,
             species_permitted == TRUE)
    
    # extract layers for the permitted species of this state
    var_lyrs <- names(results_raster)[stringr::str_detect(string = names(results_raster),            
                                                          pattern = paste(state_permitted_species$common_name, collapse = "|"))]
    state_species_raster <- subset(results_raster, var_lyrs)
    
    
    # if the state name is Florida, combine the Gulf and Atlantic shapes
    if (state_name == "Florida") {
      state_results_raster <- terra::mask(x = state_species_raster,
                                          mask = state_shapes[state_shapes$state == c("Florida Gulf","Florida Atlantic")])
    } else{
      # else just state the state shape from the state_name
      state_results_raster <- terra::mask(x = state_species_raster,
                                          mask = state_shapes[state_shapes$state == state_name])
    }
    #########
    ### Calculate mean index performance for allowed species
    state_results_permitted_index <- aggregate_index_performance_maker(species_raster = state_results_raster)
    
    # merge with all_states raster
    all_states_index_raster <- terra::merge(x = all_states_index_raster,
                                            y = state_results_permitted_index)
    
    # make the state_df from the states_results raster
    state_permitted_df <- as.data.frame(x = state_results_permitted_index,
                                        xy = TRUE,
                                        na.rm = FALSE)  %>% 
      filter(!is.na(all_species_mean_index))
    
    # add state name column
    state_permitted_df <- state_permitted_df %>% 
      mutate(state = state_name)
    
    # add to empty df of all states
    all_states_index_df <- rbind(all_states_index_df, state_permitted_df)
    
    # remove any state border rows that may have joined in df
    all_states_index_df <- all_states_index_df %>% 
      unique()
    
    # remove state_df from memory so it does not hold up calculations
    rm(state_permitted_df)
    
    #########
    ### Calculate mean index performance for all species and all species within taxa
    state_results_total_index <- all_species_aggregate_index_performance_maker(species_raster = state_results_raster)
    
    # merge with all_states raster
    all_states_total_species_index_raster <- terra::merge(x = all_states_total_species_index_raster,
                                                          y = state_results_total_index)
    
    # make the state_df from the states_results raster
    state_df <- as.data.frame(x = state_results_total_index,
                              xy = TRUE,
                              na.rm = FALSE) %>% 
      filter(!is.na(all_species_mean_index))
    
    # add state name column
    state_df <- state_df %>%
      mutate(state = state_name)
    
    # add to empty df of all states
    all_states_total_species_index_df <- rbind(all_states_total_species_index_df, state_df)
    
    # remove any state border rows that may have joined in df
    all_states_total_species_index_df <- all_states_total_species_index_df %>%
      unique()
    # remove state_df from memory so it does not hold up calculations
    rm(state_df)
    
    #########
    ### Calculate count performance for allowed species
    state_results_permitted_count <- aggregate_count_performance_maker(species_raster = state_results_raster,
                                                                       GPI_filter = 0.5)
    
    # merge with all_states raster
    all_states_count_raster <- terra::merge(x = all_states_count_raster,
                                            y = state_results_permitted_count)
    
    # make the state_df from the states_results raster
    state_df <- as.data.frame(x = state_results_permitted_count,
                              xy = TRUE,
                              na.rm = FALSE) %>% 
      filter(!is.na(all_species_count))
    
    # add state name column
    state_df <- state_df %>%
      mutate(state = state_name)
    
    # add to empty df of all states
    all_states_count_df <- rbind(all_states_count_df, state_df)
    
    # remove any state border rows that may have joined in df
    all_states_count_df <- all_states_count_df %>%
      unique()
    
    # remove state_df from memory so it does not hold up calculations
    rm(state_df)
    #########
    
    print(paste(state_name, " - DONE"))
  }
  
  ###########
  # Write index raster and df for permitted species
  # save the raster file
  terra::writeRaster(x = all_states_index_raster,
                     filename = paste0(save_path, "permitted_species_index/rasters/", "permitted_species_index_", scenario_timeperiod, ".tif"),
                     gdal="COMPRESS=NONE",
                     overwrite = overwrite)
  
  # save the data frame as a csv
  write.csv(x = all_states_index_df,
            file = paste0(save_path, "permitted_species_index/data_frames/", "permitted_species_index_", scenario_timeperiod, ".csv"))
  
  ###########
  # Write index raster and df for all species
  # save raster file
  terra::writeRaster(x = all_states_total_species_index_raster,
                     filename = paste0(save_path, "all_species_index/rasters/", "all_species_index_", scenario_timeperiod, ".tif"),
                     gdal="COMPRESS=NONE",
                     overwrite = overwrite)
  
  # save the data frame as a csv
  write.csv(x = all_states_total_species_index_df,
            file = paste0(save_path, "all_species_index/data_frames/", "all_species_index_", scenario_timeperiod, ".csv"))
  
  
  ###########
  # Write count raster and df for permitted species
  # save the raster file
  terra::writeRaster(x = all_states_count_raster,
                     filename = paste0(save_path, "permitted_species_count/rasters/", "permitted_species_count_", scenario_timeperiod, ".tif"),
                     gdal="COMPRESS=NONE",
                     overwrite = overwrite)
  
  # save the data frame as a csv
  write.csv(x = all_states_count_df,
            file = paste0(save_path, "permitted_species_count/data_frames/", "permitted_species_count_", scenario_timeperiod, ".csv"))
  
  ############
  # print that file is done
  print(paste("Done with", all_species_state_borders_list[j]))
}


```



