---
title: "species_data_and_figs_for_review"
output: html_document
date: "2024-07-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this script is to explore species specific results as requested by the reviewers of the original draft.

## Setup

Packages
```{r}
library(tidyverse)
library(terra)
library(ggplot2)
library(ggmap)
library(cowplot)
library(rnaturalearth)
library(tidyterra)
library(ggrepel)
library(ggpubr)
```

File paths
```{r}
species_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/all_species_index/"

temp_results_path <- "/home/shares/aquaculture/AOA_climate_change/pressure_prep/sst/"

save_path <- "/home/shares/aquaculture/AOA_climate_change/figures/species_plots_for_review/"

```

```{r}
test_raster <- rast(file.path(species_results_path, "all_species_245_2011_2030.tif"))

test_df <- terra::as.data.frame(x = test_raster,
                                xy = TRUE,
                                cells = TRUE,
                                na.rm = NA) %>% 
  pivot_longer(cols = 4:34,
               names_to = "species",
               values_to = str_sub(string = sources(test_raster), 
                                   start = -17,
                                   end = -5)) %>%
  mutate(species = str_remove(species,
                              pattern = "mean"),
         taxa = case_when(
           str_detect(species, "fish") ~ "fish",
           str_detect(species, "mollusc") ~ "mollusc",
           str_detect(species, "seaweed") ~ "seaweed",
           TRUE ~ "NA"
           ),
         species = str_remove(string = species,
                              patter = "__.*"))

# str_sub(string = paste0(all_species_state_borders_path, all_species_state_borders_list[j]), 
#                                  start = -17, 
#                                  end = -5)
```

make a look that does all of this for all of the species and all time periods
```{r}
# list all result raster files
raster_files <- list.files(species_results_path)

# remove current results rasters
raster_files <- raster_files[!grepl("2011_2030", raster_files)]

# read in raster of current time period
current_raster <- rast(file.path(species_results_path, "all_species_126_2011_2030.tif"))

# make base df for others to be joined to
current_df <- terra::as.data.frame(x = current_raster,
                                   xy = TRUE,
                                   cells = TRUE,
                                   # this removes rows where NAs are always present (out of stud area)
                                   na.rm = NA) %>% 
  pivot_longer(cols = 4:34,
               names_to = "species",
               # get time period and scenario for name of values
               values_to = str_sub(string = sources(current_raster), 
                                   start = -17,
                                   end = -5)) %>%
  # remove mean from species column
  mutate(species = str_remove(species,
                              pattern = "mean"),
         # make taxa column in case it is needed
         taxa = case_when(
           str_detect(species, "fish") ~ "fish",
           str_detect(species, "mollusc") ~ "mollusc",
           str_detect(species, "seaweed") ~ "seaweed",
           TRUE ~ "NA"
         ),
         # remove taxa names after species name from species column
         species = str_remove(string = species,
                              patter = "__.*")) %>% 
  dplyr::relocate(taxa, .after = species)

# make the df that will house all the results
# this will let us join the other results easily
all_times_scenarios_df <- current_df

for (i in 1:n_distinct(raster_files)) {
  # read in the next raster file from raster_files
  next_time_scenario_rast <- rast(file.path(species_results_path, raster_files[i]))
  
  # make the raster a df and process it to join
  next_time_scenario_df <- terra::as.data.frame(x = next_time_scenario_rast,
                                                xy = TRUE,
                                                cells = TRUE,
                                                # this removes rows where NAs are always present (out of stud area)
                                                na.rm = NA) %>% 
    pivot_longer(cols = 4:34,
                 names_to = "species",
                 # get time period and scenario for name of values
                 values_to = str_sub(string = sources(next_time_scenario_rast), 
                                     start = -17,
                                     end = -5)) %>%
    # remove mean from species column
    mutate(species = str_remove(species,
                                pattern = "mean"),
           # make taxa column in case it is needed
           taxa = case_when(
             str_detect(species, "fish") ~ "fish",
             str_detect(species, "mollusc") ~ "mollusc",
             str_detect(species, "seaweed") ~ "seaweed",
             TRUE ~ "NA"
           ),
           # remove taxa names after species name from species column
           species = str_remove(string = species,
                                patter = "__.*"))
  
  # join with other results
  all_times_scenarios_df <- left_join(all_times_scenarios_df,
                                      next_time_scenario_df,
                                      by = c("cell", "x", "y", "species", "taxa"))
  
  print(paste("Done with ", i))
  
}

# make the NAs zeros
all_times_scenarios_df[is.na(all_times_scenarios_df)] <- 0
```

Now calculate the differences in PI over time
```{r}
differences_species_pi <- all_times_scenarios_df %>% 
  rename(pi_current = "126_2011_2030") %>% 
  # across columns 7-15 calculate the difference between current PI and each scenario
  mutate(across(.cols = 7:15,
                .fns = ~ .x - pi_current)) %>% 
  pivot_longer(cols = 7:15,
               names_to = "scenario_time_period",
               values_to = "difference_in_pi")
```


## Temp
Now we need to make similar df for temperature

now make a loop
```{r}
current_temp_raster <- rast(file.path(temp_results_path, "sst_126_2011_2030.tif"))

current_temp_df <- terra::as.data.frame(x = current_temp_raster,
                                xy = TRUE,
                                cells = TRUE,
                                na.rm = NA) %>% 
  # only keep columns 1:4 so we can keep the mean_sst
  select(1, 2, 3, "temp" = 4) %>% 
  rename("126_2011_2030" = "temp")

temp_files <- list.files(temp_results_path,
                         # the carrot denotes to only get files that start with sst
                         pattern = "^sst")

# remove current results rasters
temp_files <- temp_files[!grepl("2011_2030", temp_files)]

#make an all_temps_df
all_temps_df <- current_temp_df

for (i in 1:n_distinct(raster_files)) {
  # read in the next raster file from raster_files
  next_time_scenario_rast <- rast(file.path(temp_results_path, temp_files[i]))
  
  rename_characters <- str_sub(string = sources(next_time_scenario_rast), 
                               start = -17,
                               end = -5)
  
  # make the raster a df and process it to join
  next_time_scenario_df <- terra::as.data.frame(x = next_time_scenario_rast,
                                                xy = TRUE,
                                                cells = TRUE,
                                                # this removes rows where NAs are always present (out of stud area)
                                                na.rm = NA) %>%
    # only keep columns 1:4 so we can keep the mean_sst
    select(1, 2, 3, "temp" = 4)  
  
  # Rename the temp column
  names(next_time_scenario_df)[names(next_time_scenario_df) == "temp"] <- rename_characters
  
    # join with other results
  all_temps_df <- left_join(all_temps_df,
                            next_time_scenario_df,
                            by = c("cell", "x", "y"))
  
  print(paste("Done with ", i))
  
}

```

Now calculate the differences in temp over time and scenario
```{r}
differences_temps <- all_temps_df %>% 
  rename(temp_current = "126_2011_2030") %>% 
  # across columns 7-15 calculate the difference between current PI and each scenario
  mutate(across(.cols = 5:13,
                .fns = ~ .x - temp_current)) %>% 
  pivot_longer(cols = 5:13,
               names_to = "scenario_time_period",
               values_to = "difference_in_temp")
```

## Join PI and temp
```{r}
pi_and_temp_change <- left_join(x = differences_species_pi,
                                y = differences_temps,
                                by = c("cell", "x", "y", "scenario_time_period"))

# save the file
write_csv(x = pi_and_temp_change,
          file = paste0(save_path, "species_pi_and_temp_diffs.csv"))
```

## Plot
