---
title: "Seaweed Taxa Maps"
output: html_document
date: "2023-08-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

The objective of this Rmd is to develop figures for the publication.

Packages
```{r}
library(tidyverse)
library(terra)
library(ggplot2)
library(ggmap)
library(cowplot)
library(rnaturalearth)
library(tidyterra)
library(ggrepel)
library(ggpubr)
```

File paths
```{r}
index_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/mean_index/"
count_results_path <- "/home/shares/aquaculture/AOA_climate_change/performance_calcs/counts/"
#state_shapes_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_shapes/"
states_list_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/state_waters/"
zeros_path <- "/home/shares/aquaculture/AOA_climate_change/spatial/zeros/rasters/"
figure_save_path <- "/home/shares/aquaculture/AOA_climate_change/figures/maps_for_each_taxa/seaweeds/"
depth_raster_path <- "/home/shares/aquaculture/AOA_climate_change/pressure_prep/"

```

Set up state outlines
```{r}
state_list <- terra::vect(x = paste0(states_list_path, "state_waters.shp"))
state_list <- state_list$state
state_list <- state_list[!str_detect(state_list, pattern = "Florida")]
state_list <- c(state_list, "Florida")



USA_state_shapes <- ne_states(iso_a2 = "US", returnclass = "sf")

USA_state_shapes <- USA_state_shapes %>% 
  select(name, postal, geometry) %>% 
  filter(stringr::str_detect(string = name,            
                    pattern = paste(state_list, collapse = "|")))

project_crs <- crs(terra::rast(x = paste0(index_results_path, "mean_index_performance_126_2011_2030.tif")))

USA_state_shapes <- terra::vect(USA_state_shapes)
crs(USA_state_shapes) <- project_crs

USA_state_shapes <- terra::crop(x = USA_state_shapes,
                                y = terra::rast(x = paste0(index_results_path, "mean_index_performance_126_2011_2030.tif")))


```

Set up the zeros data for change calculations and the depth mask
```{r}
depth_mask <- terra::rast(paste0(depth_raster_path, "depth_200m.tif" ))

zeros_data <- terra::rast(paste0(zeros_path, "federal_eez_zeros.tif"))

zeros_data <- terra::mask(x = zeros_data,
                          mask = depth_mask)

```

Data Set Up
```{r}
current_index <- terra::rast(x = paste0(index_results_path, "mean_index_performance_126_2011_2030.tif"))
current_index <- terra::mask(x = current_index,
                             mask = depth_mask)
current_index <- current_index$seaweed_mean_index
current_index_df <- as.data.frame(current_index, xy = TRUE, cells = TRUE)

current_count <- terra::rast(x = paste0(count_results_path, "count_126_2011_2030.tif"))
current_count <- terra::mask(x = current_count,
                             mask = depth_mask)
current_count <- current_count$seaweed_count
current_count_df <- as.data.frame(current_count, xy = TRUE, cells = TRUE)

# 245 Scenario
index_245_2051_2070 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_245_2051_2070.tif"))
index_245_2051_2070 <- terra::mask(x = index_245_2051_2070,
                                   mask = depth_mask)
index_245_2051_2070 <- index_245_2051_2070$seaweed_mean_index
index_245_2051_2070_df <- as.data.frame(index_245_2051_2070, xy = TRUE, cells = TRUE)


count_245_2051_2070 <- terra::rast(x = paste0(count_results_path, "count_245_2051_2070.tif"))
count_245_2051_2070 <- terra::mask(x = count_245_2051_2070,
                                   mask = depth_mask)
count_245_2051_2070 <- count_245_2051_2070$seaweed_count
count_245_2051_2070_df <- as.data.frame(count_245_2051_2070, xy = TRUE, cells = TRUE)


index_245_2071_2090 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_245_2071_2090.tif"))
index_245_2071_2090 <- terra::mask(x = index_245_2071_2090,
                                   mask = depth_mask)
index_245_2071_2090 <- index_245_2071_2090$seaweed_mean_index
index_245_2071_2090_df <- as.data.frame(index_245_2071_2090, xy = TRUE, cells = TRUE)


count_245_2071_2090 <- terra::rast(x = paste0(count_results_path, "count_245_2071_2090.tif"))
count_245_2071_2090 <- terra::mask(x = count_245_2071_2090,
                                   mask = depth_mask)
count_245_2071_2090 <- count_245_2071_2090$seaweed_count
count_245_2071_2090_df <- as.data.frame(count_245_2071_2090, xy = TRUE, cells = TRUE)

# 585 scenario
index_585_2051_2070 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_585_2051_2070.tif"))
index_585_2051_2070 <- terra::mask(x = index_585_2051_2070,
                                   mask = depth_mask)
index_585_2051_2070 <- index_585_2051_2070$seaweed_mean_index
index_585_2051_2070_df <- as.data.frame(index_585_2051_2070, xy = TRUE, cells = TRUE)


count_585_2051_2070 <- terra::rast(x = paste0(count_results_path, "count_585_2051_2070.tif"))
count_585_2051_2070 <- terra::mask(x = count_585_2051_2070,
                                   mask = depth_mask)
count_585_2051_2070 <- count_585_2051_2070$seaweed_count
count_585_2051_2070_df <- as.data.frame(count_585_2051_2070, xy = TRUE, cells = TRUE)


index_585_2071_2090 <- terra::rast(x = paste0(index_results_path, "mean_index_performance_585_2071_2090.tif"))
index_585_2071_2090 <- terra::mask(x = index_585_2071_2090,
                                   mask = depth_mask)
index_585_2071_2090 <- index_585_2071_2090$seaweed_mean_index
index_585_2071_2090_df <- as.data.frame(index_585_2071_2090, xy = TRUE, cells = TRUE)


count_585_2071_2090 <- terra::rast(x = paste0(count_results_path, "count_585_2071_2090.tif"))
count_585_2071_2090 <- terra::mask(x = count_585_2071_2090,
                                   mask = depth_mask)
count_585_2071_2090 <- count_585_2071_2090$seaweed_count
count_585_2071_2090_df <- as.data.frame(count_585_2071_2090, xy = TRUE, cells = TRUE)
```


### Map Scales
Index:
```{r}
## index maps
current_index_limits <- c(0, 0.75)
current_index_breaks <- c(0, .25, .50, .75)

change_index_limits <- c(-.10, .10)
change_index_breaks <- c(-.10, -.05, 0, .05, .10)
```

Count:
Taxa and all species scales need to be different for the count plots because they
```{r}
# setup for all species
all_species_current_count_limits <- c(0, 20)
all_species_current_count_breaks <- c(0, 5, 10, 15, 20)

all_species_change_count_limits <- c(-12, 12)
all_species_change_count_breaks <- c(-12, -6, 0, 6, 12)

# setup for taxa
taxa_current_count_limits <- c(0, 10)
taxa_current_count_breaks <- c(0, 2, 4, 6, 8, 10)

taxa_change_count_limits <- c(-12, 12)
taxa_change_count_breaks <- c(-12, -6, 0, 6, 12)

```


## Index

### Current Index
Using tidyterra

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = current_index,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "viridi" #previous palettes: "deep"
dir <- -1 # previous direction: 1

mainland_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = current_index_limits,
                        breaks = current_index_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Mean PI") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white",
                                    color = "white"),
    panel.border = element_rect(color = NA, fill = NA),
    plot.background = element_rect(fill = "white",
                                    color = "white"))+  
  ggtitle("      Seaweeds Mean Performance Index Under Current Ocean Conditions") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = current_index,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = current_index_limits,
                        breaks = current_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
#alaska_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = current_index,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = current_index_limits,
                        breaks = current_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_plot
```

```{r}
current_index_plot<-
  ggdraw() +
  draw_plot(mainland_plot) +
  draw_plot(alaska_plot, width=0.30, height=0.30,  x = 0.23, y = .495)+
  draw_plot(hawaii_plot, width=0.25, height=0.20,  x = 0.10, y = .142)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE: this plot does not look like the plot saved
# View the saved file to see the final output proportions
current_index_plot

ggsave(plot = current_index_plot,
       filename = "current_index_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### index change to ssp2 2051-2070
Data setup
```{r}
index_change_245_2051_2070 <- sum(index_245_2051_2070, zeros_data) - sum(current_index, zeros_data)
summary(index_change_245_2051_2070)

index_change_245_2051_2070 <- ifel(test = index_change_245_2051_2070 > change_index_limits[2],
                                   yes = change_index_limits[2],
                                   no = ifel(index_change_245_2051_2070 < change_index_limits[1],
                                             yes = change_index_limits[1],
                                             no = index_change_245_2051_2070))

summary(index_change_245_2051_2070)
```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = index_change_245_2051_2070,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_index_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nMean PI") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Mean Performance Index from Current Conditions\n      to SSP2 2051-2071") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_index_change_245_2051_2070_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = index_change_245_2051_2070,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_index_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
alaska_index_change_245_2051_2070_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = index_change_245_2051_2070,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_index_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
hawaii_index_change_245_2051_2070_plot
```

```{r}
index_change_245_2051_2070_plot <-
  ggdraw() +
  draw_plot(mainland_index_change_245_2051_2070_plot) +
  draw_plot(alaska_index_change_245_2051_2070_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_index_change_245_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE: this does not match the look of the saved output
index_change_245_2051_2070_plot

ggsave(plot = index_change_245_2051_2070_plot,
       filename = "index_change_245_2051_2070_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### index change to ssp2 2071-2090
Data setup
```{r}
index_change_245_2071_2090 <- sum(index_245_2071_2090, zeros_data) - sum(current_index, zeros_data) 

index_change_245_2071_2090 <- ifel(test = index_change_245_2071_2090 > change_index_limits[2],
                                   yes = change_index_limits[2],
                                   no = ifel(index_change_245_2071_2090 < change_index_limits[1],
                                             yes = change_index_limits[1],
                                             no = index_change_245_2071_2090))
```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = index_change_245_2071_2090,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_index_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nMean PI") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Mean Performance Index from Current Conditions\n      to SSP2 2071-2090") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

#mainland_index_change_245_2071_2090_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = index_change_245_2071_2090,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_index_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
#alaska_index_change_245_2071_2090_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = index_change_245_2071_2090,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_index_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_index_change_245_2071_2090_plot
```

```{r}
index_change_245_2071_2090_plot <-
  ggdraw() +
  draw_plot(mainland_index_change_245_2071_2090_plot) +
  draw_plot(alaska_index_change_245_2071_2090_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_index_change_245_2071_2090_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 
index_change_245_2071_2090_plot

ggsave(plot = index_change_245_2071_2090_plot,
       filename = "index_change_245_2071_2090_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### index change to ssp5 2051-2070
Data setup
```{r}
index_change_585_2051_2070 <- sum(index_585_2051_2070, zeros_data) - sum(current_index, zeros_data)

index_change_585_2051_2070 <- ifel(test = index_change_585_2051_2070 > change_index_limits[2],
                                   yes = change_index_limits[2],
                                   no = ifel(index_change_585_2051_2070 < change_index_limits[1],
                                             yes = change_index_limits[1],
                                             no = index_change_585_2051_2070))
```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = index_change_585_2051_2070,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_index_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nMean PI") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Mean Performance Index from Current Conditions\n      to SSP5 2051-2071") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

#mainland_index_change_585_2051_2070_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = index_change_585_2051_2070,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_index_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
#alaska_index_change_585_2051_2070_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = index_change_585_2051_2070,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_index_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_index_change_585_2051_2070_plot
```

```{r}
index_change_585_2051_2070_plot <-
  ggdraw() +
  draw_plot(mainland_index_change_585_2051_2070_plot) +
  draw_plot(alaska_index_change_585_2051_2070_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_index_change_585_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE this plot looks different than saved plot
index_change_585_2051_2070_plot

ggsave(plot = index_change_585_2051_2070_plot,
       filename = "index_change_585_2051_2070_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```

### index change to ssp5 2071-2090
Data setup
```{r}
index_change_585_2071_2090 <- sum(index_585_2071_2090, zeros_data) - sum(current_index, zeros_data) 

index_change_585_2071_2090 <- ifel(test = index_change_585_2071_2090 > change_index_limits[2],
                                   yes = change_index_limits[2],
                                   no = ifel(index_change_585_2071_2090 < change_index_limits[1],
                                             yes = change_index_limits[1],
                                             no = index_change_585_2071_2090))

summary(index_change_585_2071_2090)

```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = index_change_585_2071_2090,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_index_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nMean PI") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Mean Performance Index from Current Conditions\n      to SSP5 2071-2090") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_index_change_585_2071_2090_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = index_change_585_2071_2090,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_index_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
alaska_index_change_585_2071_2090_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = index_change_585_2071_2090,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_index_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = change_index_limits,
                        breaks = change_index_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_index_change_585_2071_2090_plot
```

```{r}
index_change_585_2071_2090_plot <-
  ggdraw() +
  draw_plot(mainland_index_change_585_2071_2090_plot) +
  draw_plot(alaska_index_change_585_2071_2090_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_index_change_585_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE this plot looks different than saved plot
index_change_585_2071_2090_plot

ggsave(plot = index_change_585_2071_2090_plot,
       filename = "index_change_585_2071_2090_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


## count
pretty much do the exact same as above but use count data

### Current Count
mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# add in the zeros data for count graphing
current_count <- sum(current_count, zeros_data, na.rm = TRUE)

# load main raster
mainland_raster <- crop(x = current_count,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "viridi" #previous palettes: "deep"
dir <- -1 # previous direction: 1

mainland_current_count <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_current_count_limits,
                        breaks = taxa_current_count_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Species \nCount") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    # background color
    panel.background = element_rect(fill = "white",
                                    color = "white"),
    panel.border = element_rect(color = NA, fill = NA),
    plot.background = element_rect(fill = "white",
                                    color = "white")) +  
  ggtitle("      Seaweeds Viable Species Count Under Current Ocean Conditions") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_current_count
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster_count <- crop(x = current_count,
                            y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_current_count <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster_count) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = "deep",
                        direction = 1,
                        limits = taxa_current_count_limits,
                        breaks = taxa_current_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
alaska_current_count
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster_count <- crop(x = current_count,
                            y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_current_count <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster_count) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = "deep",
                        direction = 1,
                        limits = taxa_current_count_limits,
                        breaks = taxa_current_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
hawaii_current_count
```

```{r}
count_current_plot <- ggdraw() +
  draw_plot(mainland_current_count) +
  draw_plot(alaska_current_count, width=0.30, height=0.30,  x = 0.23, y = .495)+
  draw_plot(hawaii_current_count, width=0.25, height=0.20,  x = 0.10, y = .142)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

count_current_plot

ggsave(plot = count_current_plot,
       filename = "count_current_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### count change to ssp2 2051-2070
Data setup
```{r}
count_change_245_2051_2070 <- sum(count_245_2051_2070, zeros_data, na.rm = TRUE) - sum(current_count, zeros_data, na.rm = TRUE)
```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = count_change_245_2051_2070,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_count_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nCount") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Viable Species Count Under Current Ocean Conditions\n      to SSP2 2051-2071") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

#mainland_count_change_245_2051_2070_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = count_change_245_2051_2070,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_count_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)

#alaska_count_change_245_2051_2070_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = count_change_245_2051_2070,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_count_change_245_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_count_change_245_2051_2070_plot
```

```{r, warning=FALSE}
count_change_245_2051_2070_plot <-
  ggdraw() +
  draw_plot(mainland_count_change_245_2051_2070_plot) +
  draw_plot(alaska_count_change_245_2051_2070_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_count_change_245_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE: this does not match the look of the saved output
count_change_245_2051_2070_plot

ggsave(plot = count_change_245_2051_2070_plot,
       filename = "count_change_245_2051_2070_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### count change to ssp2 2071-2090
Data setup
```{r}
count_change_245_2071_2090 <- sum(count_245_2071_2090, zeros_data, na.rm = TRUE) - sum(current_count, zeros_data, na.rm = TRUE)

```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = count_change_245_2071_2090,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_count_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nCount") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Viable Species Count Under Current Ocean Conditions\n      to SSP2 2071-2090") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_count_change_245_2071_2090_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = count_change_245_2071_2090,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_count_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
#alaska_count_change_245_2071_2090_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = count_change_245_2071_2090,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_count_change_245_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_count_change_245_2071_2090_plot
```

```{r, warning=FALSE}
count_change_245_2071_2090_plot <-
  ggdraw() +
  draw_plot(mainland_count_change_245_2071_2090_plot) +
  draw_plot(alaska_count_change_245_2071_2090_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_count_change_245_2071_2090_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 
count_change_245_2071_2090_plot

ggsave(plot = count_change_245_2071_2090_plot,
       filename = "count_change_245_2071_2090_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```


### count change to ssp5 2051-2070
Data setup
```{r}
count_change_585_2051_2070 <- sum(count_585_2051_2070, zeros_data, na.rm = TRUE) - sum(current_count, zeros_data, na.rm = TRUE)

```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = count_change_585_2051_2070,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_count_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nCount") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Viable Species Count Under Current Ocean Conditions\n      to SSP5 2051-2071") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

#mainland_count_change_585_2051_2070_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = count_change_585_2051_2070,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_count_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
#alaska_count_change_585_2051_2070_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = count_change_585_2051_2070,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_count_change_585_2051_2070_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_count_change_585_2051_2070_plot
```

```{r, warning=FALSE}
count_change_585_2051_2070_plot <-
  ggdraw() +
  draw_plot(mainland_count_change_585_2051_2070_plot) +
  draw_plot(alaska_count_change_585_2051_2070_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_count_change_585_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE this plot looks different than saved plot
count_change_585_2051_2070_plot

ggsave(plot = count_change_585_2051_2070_plot,
       filename = "count_change_585_2051_2070_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```

### count change to ssp5 2071-2090
Data setup
```{r}
count_change_585_2071_2090 <- sum(count_585_2071_2090, zeros_data, na.rm = TRUE) - sum(current_count, zeros_data, na.rm = TRUE)
```

mainland
```{r, warning = FALSE}
# xlow, xhigh, ylow, yhigh
mainland_ext <- c(-127, -60, 24, 50)

# load main raster
mainland_raster <- crop(x = count_change_585_2071_2090,
                        y = mainland_ext)

# remove non-mainland states
mainland_states <- USA_state_shapes %>% 
  filter(!name %in% c("Alaska", "Hawaii"))

# retrieve small states centroids for labeling
MD_DE_NJ_RI <- mainland_states %>% 
  filter(name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")) %>% 
  centroids() %>% 
  as.data.frame(geom = "XY")

# Choose palette and direction for maps
pal <- "muted" #previous palette: "bl_yl_rd"
dir <- -1 # previous direction: -1

mainland_count_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = mainland_raster) +
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        #background color fill
                        na.value = "grey80",
                        name = "Change \nCount") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) + 
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) +  
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = mainland_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  theme(# change the legend position and direction
    legend.position = c(.9,.3),
    legend.direction = "vertical",
    plot.title.position = "panel",
    # background color
    panel.background = element_rect(fill = "white", 
                                    color = NA),
    panel.border = element_rect(colour = NA, fill=NA))+  
  ggtitle("      Change in Seaweeds Viable Species Count Under Current Ocean Conditions\n      to SSP5 2071-2090") +
  # add in labels for states
  geom_spatvector_text(data = mainland_states %>% 
                         filter(!name %in% c("Maryland", "Delaware", "New Jersey", "Rhode Island")),
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5)+
  # add in labels for states that need to be moved a bit
  geom_text_repel(data = MD_DE_NJ_RI,
                  aes(x = x,
                      y = y,
                      label = postal),
                  # order of nudges: MD, DE, NJ, RI
                  nudge_x = c(-1.5,-1, -0.5,0),
                  nudge_y = c(1.5,1.5,1.5,-1.5),
                  alpha = 0.5,
                  size = 2.5) 

mainland_count_change_585_2071_2090_plot
```

Alaska
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
alaska_ext <- c(-188, -129, 50, 94)

alaska_raster <- crop(x = count_change_585_2071_2090,
                      y = alaska_ext)

# isolate Alaska shape
alaska_states <- USA_state_shapes %>% 
  filter(name %in% c("Alaska"))

alaska_count_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = alaska_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = alaska_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"))+  
  #make a border
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.25)) +
  # add in the alaska label
  geom_spatvector_text(data = alaska_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1)
alaska_count_change_585_2071_2090_plot
```

Hawaii
```{r, warning=FALSE}
# xlow, xhigh, ylow, yhigh
hawaii_ext <- c(-166, -154, 15, 25)

hawaii_raster <- crop(x = count_change_585_2071_2090,
                      y = hawaii_ext)
# isolate Hawaii shape
hawaii_states <- USA_state_shapes %>% 
  filter(name %in% c("Hawaii"))

hawaii_states <- crop(x = hawaii_states,
                      y = hawaii_ext)

hawaii_count_change_585_2071_2090_plot <- ggplot() +
  # pull in the raster data
  geom_spatraster(data = hawaii_raster) +
  # fill in scale details and color of background
  scale_fill_whitebox_c(palette = pal,
                        direction = dir,
                        limits = taxa_change_count_limits,
                        breaks = taxa_change_count_breaks,
                        # background color fill
                        na.value = "grey80") +
  #remove x y breaks
  scale_x_continuous(labels = NULL, breaks = 0) +
  scale_y_continuous(labels = NULL, breaks = NULL, n.breaks = 0) + 
  # remove x y labels as they are coordinates
  labs(x = "",
       y = "") +
  # add in the state boundary lines
  geom_spatvector(data = hawaii_states,
                  alpha = 0.6,
                  fill = "white",
                  color = "#7d7d7d") +
  theme_void()+
  # don't show the legend since we are adding this to our mainland figure
  theme(legend.position = "none",
        # background color
        panel.background = element_rect(fill = "grey80"),
        # add in a border
        panel.border = element_rect(colour = "black", fill=NA, size=0.25))+  
  geom_spatvector_text(data = hawaii_states,
                       aes(label = postal),
                       alpha = 0.5,
                       size = 2.5,
                       nudge_y = 1,
                       nudge_x = -8)
#hawaii_count_change_585_2071_2090_plot
```

```{r, warning = FALSE}
count_change_585_2071_2090_plot <-
  ggdraw() +
  draw_plot(mainland_count_change_585_2071_2090_plot) +
  draw_plot(alaska_count_change_585_2071_2090_plot, width=0.30, height=0.30,  x = 0.23, y = .475)+
  draw_plot(hawaii_count_change_585_2051_2070_plot, width=0.25, height=0.20,  x = 0.10, y = .122)+
  theme(panel.background = element_rect(fill = 'white',
                                        color = "white"),
        plot.background = element_rect(fill = 'white',
                                        color = "white")) 

# NOTE this plot looks different than saved plot
count_change_585_2071_2090_plot

ggsave(plot = count_change_585_2071_2090_plot,
       filename = "count_change_585_2071_2090_plot.pdf",
       device = "pdf",
       path = figure_save_path,
       width = 7,
       height = 5,
       units = "in")
```